Summary Statistics

### 2025-02-10 application_examples/abc_inferences/draft-abc-inferences-vignette.Rmd
Addinf filter_CpG_count.R

1. Save as simulation design the genomic structure, tree(s) -- GIVEN -- and sampled parameter combinations.

>>>>

1. Set the output directory.

2. Get the CpG count in islands and non-island regions.

3. Filter CpG count to keep only regions with at least one CpG site and get the CpG position indeces for each region.

1. Save as simulation design the genomic structure for the regions within the selected genomic region, tree(s) -- GIVEN -- and sampled parameter combinations.

### 2025-02-10 extensive_tests/draft-sumstat-vignette.Rmd
Addinf filter_CpG_count.R

$$
\hat{\sigma}(w)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(w) \\
\hat{\sigma}(z)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(z) \\
$$

@@

@@

get_FChange_cherryData (uses find_cherries --get_cherryDist-- and cherry_diffs -- now count_cherryMethDiff )

NOTE: Summary statistics related with tree cherries require a tree with tip labels givenas numeric values

>>>>

$$
\hat{\sigma}(w)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(w) \\
\hat{\sigma}(z)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(z) \\
$$
These values can be computed with the functions `get_islandSDFreqP`, `get_nonislandSDFreqP`,`get_islandSDFreqM` and `get_nonislandSDFreqM` as in the following examples:

@@

These values can be computed with the functions `compute_meanCor_i` for island structures and `compute_meanCor_ni` for non-island structures as in the following examples:

@@

Functions:

- `get_cherryDist` to get the distances between the cherry tips.
